Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-23 WRITEUP/ms.tex
update ref

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0$-$1. It is clear that RXJ1131 has a gas-rich companion, but how does
this affect its internal dynamics and what is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.
While our result is consistent with previous studies of RXJ1131, this
contrast strongly with studies of mergers, where powerful AGN are
usually found in late stage mergers (Yuan+10, Iwasawa+11) and
that only major mergers near their final
coalescence can power/provide \LIR\,$>$\,10$^{12}$\,\Lsun, based on
a recent study of a sample of 65 local U/LIRGs
(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1; Larson+16).
If this is also the case at $z$$\sim$0.65, this would imply RXJ1131
is a major merger near its final coalescence and that the spatially offset
component is an expulsion of gas driven by AGN winds or is some
tidally ejected material from previous passage.
In that case, the molecular gas fraction in the host
galaxy should have declined (as in ellipticals) compared to early
stage mergers (can we find molecular gas mass fraction as a
function of merger stage?) and that the molecular gas would
be more concentrated in the nuclear region.
This is inconsistent with what
is observed (which strongly favors a disk morphology; 
but there are outliers --  Ueda+14 find
extended molecular gas in merger remnant) and
the fact that there is on-going \SF activity.
Hence, we reject this and speculate the discrepancy is a consequence
of (the power source of) IR luminous galaxies are already very different by this redshift.
An alternative explanation might be that the
CO is less strongly-magnified as compared to the dust emission,
in which case, the lensing-corrected \LFIR is overestimated.
This is plausible given the extent of the source with respect to the caustics
and that substantial differential lensing effect has been seen across CO and other
wavelengths. If we instead use the NIR ($H$-band) magnification factor ($\mu_{\rm L}$\,=\,BLAH; C06), 
we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is consistent with a minor
merger in the context of the results reported by Larson+16.

>>>>

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0$-$1. It is clear that RXJ1131 has a gas-rich companion, but how does
this affect its internal dynamics and what is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.

While our result is consistent with other studies of RXJ1131, it
contrast strongly with studies of local (U)LIRGs/mergers
(\LIR\,=\,10$^{11-12.5}$\,\Lsun; $z$\,$<$\,0.1), where active AGN are
typically found in late stage mergers
\citep{Yuan10a,Iwasawa11a,Carpineti12a} and
that only major mergers near their final
coalescence can provide \LIR\,$>$\,10$^{12}$\,\Lsun,
\citep[\eg][]{Carpineti15a,Larson16a}.
If this is also the case at $z$$\sim$0.65, this would imply RXJ1131
is a major merger near its final coalescence and that the spatially offset
component is an expulsion of gas driven by AGN winds or is some
tidally ejected material from previous passage.
In that case, the molecular gas fraction in the host
galaxy should have declined (as in ellipticals) compared to early
stage mergers (can we find molecular gas mass fraction as a
function of merger stage?) and that the molecular gas would
be more concentrated in the nuclear region.
This is inconsistent with what
is observed (which strongly favors a disk morphology;
but there are outliers --  \citet{Ueda14a} find
extended molecular gas in merger remnant) and
the fact that there is on-going \SF activity.
Hence, we reject this and speculate the discrepancy is a consequence
of (the power source of) IR luminous galaxies are already very different by this redshift.

An alternative explanation might be that the
CO is less strongly-magnified as compared to the dust emission,
in which case, the lensing-corrected \LFIR is overestimated.
This is plausible given the extent of the source with respect to the caustics
and that substantial differential lensing effect has been seen across CO and other
wavelengths. If we instead use the NIR ($H$-band) magnification factor ($\mu_{\rm L}$\,=\,BLAH; C06),
we find \LFIR\,=\,BLAH. This would imply that RXJ1131 is consistent with a minor
merger in the context of the results reported by \citet{Carpineti15a} and \citet{Larson16a}.
